\documentclass[../cookbook.tex]{subfiles}
\begin{document}
\begin{recipe}{Lilac Simple Syrup}[multi]

\blurb{If you don't add the purple food coloring, it will look yellow/brown, but when added to something like lemonade, it will turn the lemonade pink/purple.}
\yield{2 cups simple syrup}
\acttime{20-30 minutes}
\inacttime{3-8 hours}
\source{Spruce Eats}
\ingredients
	{4c Lilac Flowers}
	{2c Water}
	{2c Sugar}
	{\textbf{Optional:} a couple of drops of purple food coloring}
\stopingredients
\preparation
	{Rinse the lilac blossoms under cold water to clean off dust/pollen/bugs.}
	{Add the water and sugar to a medium saucepan and heat on medium until the sugar has dissolved and the syrup is clear.}
	{Reduce heat to low and add the lilacs. Cover the pan and heat for five minutes.}
	{Remove from heat and let steep for at least 3 hours or up to overnight.}
	{Strain and squeeze as much liquid from the flowers as possible.}
	{Add the food coloring if using.}
	{Place in airtight container and refrigerate for up to a month.}
\stopprep
\end{recipe}
\vspace{1 in}
\begin{recipe}{Lilac Cocktail}
\source{\url{https://emilyfabulous.com}}
\blurb{I am as surprised as you are that this doesn't have a better name.}
\ingredients
    {2 oz gin}
    {1 oz lemon juice}
    {1 oz lilac syrup}
    {1 egg white}
\stopingredients
\preparation
    {Add the gin, lemon juice, lilac syrup, and egg white to a cocktail shaker. Dry shake (no ice) to create a foam}
    {Add fresh ice and shake again.}
    {Strain into a cocktail glass.}
\stopprep
\end{recipe}
\begin{recipe}{Hot Chocolate}
\source{Cooking Light}
\begin{center}
\acttime{15-20 minutes}
\yield{4 mugs of hot cocoa}
\end{center}
\ingredients
    {\sfrac{2}{3} c boiling water}
    {2 oz dark/bittersweet (60-70\% cocoa) chocolate, finely chopped}
    {1 \sfrac{1}{3} c milk}
    {1 cup espresso or strong coffee}
    {\sfrac{1}{4} c cocoa powder}
    {\sfrac{1}{4} c packed brown sugar}
    {1 2-inch strip orange rind}
    {\textbf{Optional:} whipped cream}
\stopingredients
\preparation
    {Combine the boiling water and chopped chocolate in a medium saucepan, stirring until the chocolate melts.}
    {Add milk, coffee, cocoa powder, brown sugar, and orange rind. Cook over medium-low heat, stirring with a whisk, for five minutes or until tiny bubbles form around the edge of the pan, stirring frequently (do not boil)}
    {Discard the orange rind and pour into 4 mugs.}
    {Top with whipped cream if desired.}
\stopprep
\end{recipe}
\begin{recipe}{Black Walnut Social}
\source{\url{https://emilyfabulous.com}}
\ingredients
{2 oz gin (barrel aged or Old Tom if possible)}
{1 oz cardamaro}
{3-4 dashes black walnut bitters}
{\sfrac{3}{4} oz lemon juice}
{orange peel for garnish}
\stopingredients
\preparation
{Place a large ice cube into a rocks glass.}
{Add the gin, cardamaro, bitters, and lemon juice to a mixing glass with ice and stir.}
{Strain into the rocks glass, garnish with the orange peel.}
\stopprep
\end{recipe}

\end{document}
