\documentclass[../cookbook.tex]{subfiles}

\begin{document}
\begin{recipe}{Fish Stew}

\blurb{To reheat this, do not microwave it. Instead, stick it in a pot over medium-low heat.}
\yield{4 servings?}
\acttime{15 minutes}
\inacttime{30 minutes}
\source{\url{https://www.simplyrecipes.com}}

\ingredients
{6 Tbsp olive oil}
{1 medium onion, chopped}
{3 (or 6) cloves garlic, minced}
{\sfrac{2}{3} c fresh parsley, chopped}
{14 oz can crushed or diced tomatoes (or 1 \sfrac{1}{2}c fresh tomato, chopped)}
{2 tsp tomato paste}
{8 oz clam juice (1 c shellfish stock if you can't find that)}
{\sfrac{1}{2} c dry white wine}
{1 \sfrac{1}{2} lb firm white fish (halibut, cod, pollock, snapper, etc.)}
{dried oregano, to taste (start with a pinch)}
{dried thyme, to taste (start with a pinch)}
{\sfrac{1}{8} tsp hot sauce, or more to taste (more)}
{\textbf{Optional:} It could be good to add some combination of chorizo, potatoes, kale, and carrots to this.}
{salt and pepper, to taste}
\stopingredients

\preparation
{Heat olive oil in a dutch oven over medium-high heat. Add the onion and cook for 4-6 minutes, until soft}
{Add the parsley and cook for 1 minute, stirring constantly}
{Add the garlic and cook for 1 minute or until fragrant, stirring constantly}
{Add tomatoes and tomato paste and cook for about 10 minutes, stirring occasionally}
{Add the clam juice, wine, and fish, and bring to a simmer. Cook for 3 to 5 minutes, until the fish is cooked through and flaky.}
{Season with salt, pepper, oregano, thyme, and hot sauce}
\stopprep
\end{recipe}

\begin{recipe}{Kielbasa Bean Soup}
\acttime{30 minutes-ish}
\inacttime{1 hour or 8 hours (See note)}
\source{Credit where it's due: This originally came from Weight Watchers I think?}

\blurb{For a long time I made this in the slow cooker. That was a tasty method!
The last time that I made it, I did it in the dutch oven in about an hour and a
half, and I think it tasted better that way. I will give two separate preparation
sections for this recipe.}

\ingredients
	{56+ oz chicken broth (either 4 15 oz cans or 2 32 oz boxes or ?)}
	{16 oz smoked sausage (kielbasa is best) cut in half, then sliced}
	{16 oz can pinto beans, drained and rinsed}
	{16 oz can black beans, drained and rinsed}
	{4 medium carrots, chopped}
	{3 stalks celery, finely chopped (I would exclude it but I do think it makes the soup better.)}
	{1 large onion, chopped}
	{1 tsp dried or 1 Tbsp fresh thyme (do not use thyme powder)}
	{28 oz can crushed tomatoes (or 2 14.5 oz cans diced tomatoes, undrained)}
	{Salt and pepper, to taste}
\stopingredients
\textbf{If you're using the slow cooker:} \bigbreak
\preparation
	{Mix all ingredients, except for the tomatoes, in a 5 to 6 quart slow cooker. 
	Season, then cover and cook on low for 8 to 10 hours, or until the beans are
	tender and you're getting hungry.}
	{Stir in tomatoes, cover, and cook on high for 30 minutes more.}
\stopprep
\vspace{2em}

\textbf{If you're not using the slow cooker:} \bigbreak
\preparation
	{Add a tablespoon of oil to the pan, then add the mirepoix. Cook until soft
	and fragrant}
	{Add the broth and the thyme and bring to a boil, then reduce to a simmer}
    {Add the beans and the sausage and cook for 1 hour, or until the beans are
	tender}
	{Add in the tomatoes and cook for 15 minutes on medium-low heat}
\stopprep
\end{recipe}

\end{document}
